Crystal as a thermodynamic computer

### 2024-09-05 paper/main.tex
update

Improving the energy efficiency of computation is a major challenge in the development of future computing systems.
The thermodynamic computer (TC)~\cite{conte2019thermodynamic} is a new type of computer that uses thermodynamics to perform computation.
Instead of performing the computation deterministically, TCs are stochastic and are driven by thermodynamics.
Physical implementations of TCs include DNA machines~\cite{tanaka2005design}, memristors~\cite{yang2013memristive, wang2017memristors, kumar2017chaotic, wang2018fully}, and Ising machines~\cite{gu2012encoding, lucas2014ising, mohseni2022ising, fabre2014optical}.

The computational process of TCs utilizes the tendency of a physical system to evolve towards the state with the lowest free energy.
By manipulating the minimum free energy state of the system, the computation can be performed.
The change of free energy minimum state can be achieved by changing the distribution of the particles in the system, such as in the case of DNA machines~\cite{Feynman2018} or lowering the temperature of the system, such as in the case of Ising machines~\cite{boixo2013experimental}.
The former is known as the Brownian machine, which evolves the system toward the direction of the entropy increase, while the latter are energy based, which evolves the system toward the direction of the energy decrease.
\jinguo{What category are the memristors?} \ym{Memristors are energy based, which evolves the system toward the direction of the energy decrease.}

@@

@@

\subsection{Computing by cooling}\label{local-cooling}

\begin{hyp}
Let $\mathcal{P}$ be a circuit SAT problem, and $\mathcal{E}$ be an energy modeling encoding of $\mathcal{P}$ (locally). There exists a subset of $\mathcal{E}$ that exhibits the overlap gap property~\cite{Gamarnik2021}.
\end{hyp}
The overlap gap property is a property for describing the algorithmic intractability in random structures, which is based on the topological disconnectivity property of the set of pair-wise distances of near optimal solutions.
If the energy landscape of a optimization problem exhibits the overlap gap property, then it can not be solved by any local algorithms in polynomial time, including the simulated annealing method used in this work.
The intuition comes from the energy model encoding of the identity circuit.
Given a circuit with $n$ bits, the ground state degeneracy of the corresponding energy model is at least $2^n$.
The energy model can be vertically stacked $n$ copy gadgets.
Let the circuit depth be $d \sim 2^{\gamma \sqrt{n}}$ for some constant $\gamma > 0$.
The Hamming distance between two degenerate ground states for different input signals is at least $d$, which is exponential to $n$. Let us define the size of the problem as $d\times n$, then this distance is clearly linear to the problem size. We left the rigorous proof of this hypothesis to mathematicians.

@@

There is no solution with 4-atoms spin-glass that can satisfy the
constraints. The minimum number of atoms required to satisfy the
constraints is 5. We set the target states to

>>>>

Improving the energy efficiency of computation is a major challenge in the development of future computing systems.
The thermodynamic computer (TC)~\cite{conte2019thermodynamic} is a new type of computer that uses thermodynamics to perform computation.
Instead of performing the computation deterministically, TCs are stochastic and are driven by thermodynamics.
Physical implementations of TCs include DNA machines~\cite{tanaka2005design} and Ising machines~\cite{gu2012encoding, lucas2014ising, mohseni2022ising, fabre2014optical}.
% memristors~\cite{yang2013memristive, wang2017memristors, kumar2017chaotic, wang2018fully},

The computational process of TCs utilizes the tendency of a physical system to evolve towards the state with the lowest free energy.
By manipulating the minimum free energy state of the system, the computation can be performed.
The change of free energy minimum state can be achieved by changing the distribution of the particles in the system, such as in the case of DNA machines~\cite{Feynman2018} or lowering the temperature of the system, such as in the case of Ising machines~\cite{boixo2013experimental}.
The former is known as the Brownian machine, which evolves the system toward the direction of the entropy increase, while the latter are energy based, which evolves the system toward the direction of the energy decrease.

@@

\begin{hyp}
Let $\mathcal{P}$ be a circuit SAT problem, and $\mathcal{E}$ be an energy modeling encoding of $\mathcal{P}$ (locally). There exists a subset of $\mathcal{E}$ that exhibits the overlap gap property~\cite{Gamarnik2021}.
\end{hyp}
\jinguo{Leave this issue to Maddie}
The overlap gap property is a property for describing the algorithmic intractability in random structures, which is based on the topological disconnectivity property of the set of pair-wise distances of near optimal solutions.
If the energy landscape of a optimization problem exhibits the overlap gap property, then it can not be solved by any local algorithms in polynomial time, including the simulated annealing method used in this work.
The intuition comes from the energy model encoding of the identity circuit.
Given a circuit with $n$ bits, the ground state degeneracy of the corresponding energy model is at least $2^n$.
The energy model can be vertically stacked $n$ copy gadgets.
Let the circuit depth be $d \sim 2^{\gamma \sqrt{n}}$ for some constant $\gamma > 0$.
The Hamming distance between two degenerate ground states for different input signals is at least $d$, which is exponential to $n$. Let us define the size of the problem as $d\times n$, then this distance is clearly linear to the problem size. We left the rigorous proof of this hypothesis to mathematicians.

@@

@@

We set the $S_{\text{min}}$ to be the eight degenerate ground states of the spin-glass model to implement the $110$ rule.
This is overly strict, as we do not consider the case that the ground states for different input signals to have degeneracy.
The minimum number of atoms required to satisfy the
constraints is 5. We set the target states to
